The KMOS Deep Survey (KDS): dynamical measurements of $z\sim3.5$ main sequence galaxies\thanks{Based on observations obtained at the Very Large Telescope of the European Southern Observatory. Programme IDs: }

### 2017-03-29 paper.tex
Post Jim

\subsubsection{SED fitting and main-sequence}\label{subsubsec:sed_fitting}
In order to constrain their SFRs and stellar masses, the available photometry for the KDS targets was analysed using the SED fitting software described in \cite{McLure2011} and \cite{McLeod2015}.
The photometry for each target was fit with the same set of solar metallicity BC03 \citep{Bruzual2003} templates recommended for reproducing the properties of star-forming galaxies by \cite{Wuyts2011a}, and derived stellar masses and SFRs were based on a Chabrier IMF.
During the SED fitting process, dust attenuation was accounted for using the \cite{Calzetti2000} reddening law, with dust attenuation allowed to vary freely within the range $0.0<A_{V}<2.5$.
Based on the adopted template set, the median stellar mass for the full observed sample is $\log(M_{\star}/{\rm M}_{\odot}) = 10.0$. 
We note that fitting the photometry of the KDS targets with 0.2Z$\odot$ templates, rather than solar metallicity templates, typically reduces the derived stellar masses by $\simeq0.1$ dex, but this change does not affect the conclusions of this work.
In SSA22, 29 targets (36\% of the full KDS sample) do not have robust SFR measurements due to being undetected at $\geq 2\sigma$ significance in the available $J-$ and $K-$band photometry. \\

@@

\subsubsection{Half-light radii}\label{subsubsection:half-light_radii}
The half-light radius, $R_{1/2}$, provides an indication of the disk sizes and hence gives us a common fiducial distance from the centre of the galaxy at which to extract rotation velocities.
As discussed throughout the introduction and in Appendix \ref{app:comparison_samples}, methods used to derive the intrinsic maximum circular velocity, $V_{C}$, vary widely between studies, and so to compare with previous work it is necessary to extract kinematic parameters consistently from the derived rotation curves.
Knowledge of $R_{1/2}$ gives a well defined and consistent point across the extent of the galaxy at which to extract velocities, which is important when making comparisons to previous IFU studies and see Appendix \ref{app:comparison_samples} and \citep[e.g.][]{ForsterSchreiber2009,Epinat2012,Wisnioski2015,Stott2016,Harrison2017,Swinbank2017}.
Throughout our dynamical modelling and beam smearing correction (see \cref{subsec:3d_modelling}) we also require the $R_{1/2}$ value for each galaxy.
The median difference between the derived $R_{1/2}$ values and those presented in \cite{VanderWel2012} for the 22 matched GOODS-S galaxies is $\Delta R_{1/2} = 0.0054^{\prime\prime}$ (corresponding to 0.04kpc at $z\simeq3.5$).

@@

Each 0.1$^{\prime\prime}$ spaxel across a datacube is considered in turn.
The redshift value determined from fitting the [O~{\sc III}]$\lambda$5007 line in the integrated galaxy spectrum, $z_{sys}$, is used to determine the central wavelength of the redshifted [O~{\sc III}]$\lambda$5007 line, $\lambda_{obs_{5007}}$. 
We search a narrow region around $\lambda_{obs_{5007}}$ for the peak flux, assumed to correspond to the ionised gas emission, and extract a 5$\AA$ region (corresponding to 20 spectral elements) centred on this peak.
This truncated spectrum is then used in the fitting procedure for each spaxel.
The width of the extraction region is large enough to encompass unphysically large velocity shifts, but not so large as to compromise the fitting by potentially encompassing regions of the spectrum plagued by strong sky line residuals.
A single gaussian model is fit to the extraction region, again using {\tt LMFIT} \citep{Newville2014}, returning the values of the best fitting flux, $F_{g}$, central wavelength, $\lambda_{g}$, and dispersion, $\sigma_{g}$.
These parameters, along with the estimate of the noise in the datacube, are used to assess whether the fitting of the [O~{\sc III}]$\lambda$5007 line is acceptable or not. 
The noise is estimated by masking all datacube spaxels containing object flux and computing the standard deviation of the flux values in the spectral extraction region for all remaining spaxels inwards of 0.3$^{\prime\prime}$ from the cube boundary (over the same spectral region as considered to find the peak object flux).
This boundary constraint is to mitigate edge effects, where the noise increases sharply due to fewer individual exposures constituting the final stack in these regions.
The final noise value is then taken as the standard deviation of the results from each unmasked spaxel, as shown in Equation \ref{eq:noise} where $F_{i,background}$ are the flux values across the spatial regions containing no object flux and the spectral extraction region and $N_{m}$ denotes noise estimated from masking the datacube.

@@

    \caption{We plot here the kinematic grids for one rotation-dominated galaxy (top grid), one dispersion-dominated galaxy (middle grid) and one merger candidate (bottom grid) (see \protect\cref{subsec:morpho-kin-class}) from the KDS.
    In Appendix \protect\ref{app:kinematics_plots} we include these plots for each of the spatially-resolved galaxies in the KDS, divided into rotation-dominated, dispersion-dominated and merger categories.
    For each galaxy we plot on the top row the {\em HST} image, {\tt GALFIT} model and {\tt GALFIT} residuals, along with the observed [O~{\sc III}]$\lambda$5007 intensity map and velocity dispersion map. 
    On the bottom row we plot the observed velocity map, the beam-smeared model velocity and data-model velocity residuals with colour bar limits tuned to the velocity model.
    The solid black line and dashed orange line plotted in various panels show $PA_{kin}$ and $PA_{morph}$ respectively.
    Also on the bottom row, we plot extractions along $PA_{kin}$ for both the velocity and velocity dispersion.
    The grey points with errorbars on the velocity extraction plot are from the observed velocity map, the blue line and blue shaded regions represent the beam-smeared model fit to the data and errors respectively, whereas the red line and shaded regions are the intrinsic model from which $V_{C}$ is extracted.
    The purple symbols represent the extraction along $PA_{kin}$ from the residual map and the red and blue dashed lines denote the intrinsic and convolved $2R_{1/2}$ values respectively, with $V_{C}$ extracted at the intrinsic value and $V_{BS}$ extracted at the convolved value of the intrinsic and observed profiles respectively.
    The intrinsic models flatten at small radii, and so small changes in $R_{1/2}$ have negligible impact on the final, extracted $V_{C}$ values.
    The blue points on the velocity dispersion extraction plot show the values extracted from the observed dispersion map and the red are from the beam-smearing corrected map as per Equation \protect\ref{eq:dispersion_comp}.
    Also on the 1D dispersion plot we include with the blue and red dot-dash horizontal lines median values of the observed and intrinsic (i.e. $\sigma_{int}$) dispersion maps respectively.
    The merger candidate in the bottom grid requires several {\tt GALFIT} components to describe the data, mimics rotation from a purely kinematic perspective and we plot the 1D extractions without beam-smearing corrections, which are not warranted for multiple component objects.}
    \label{fig:main_body_kinematic_grids}

@@

The MCMC sampling provides a distribution of parameter values around those which give the maximum likelihood.
We have confirmed also by examining the individual parameter chains that the MCMC run has been properly `burned-in' and that the parameter estimates have converged around the 50th percentile values.
The 16th and 84th percentiles of these distributions will be used to assess the model uncertainties as described in Appendix \ref{appsubsec:model_errors}.

@@

\subsubsection{Beam-smearing corrected rotation velocities}\label{subsubsec:beam_smearing_corrected_velocities}
The intrinsic velocity, $V_{C}$, is found by reading off from the best fitting intrinsic 2D model grid at the intrinsic $2R_{1/2}$ value ($\simeq3.4R_{D}$, where $R_{D}$ is the scale length for an exponential disk).
This extraction radius is shown with the vertical red dashed line in the panels of Figure \ref{fig:main_body_kinematic_grids} showing the 1D velocity extraction.
The $V_{C}$ value extracted at $2R_{1/2}$ is a commonly used measure of the `peak' of the rotation curve \citep[e.g.][]{Miller2011,Stott2016,Pelliccia2017,Harrison2017,Swinbank2017} and extracting the velocity at $\geqslant 2R_{1/2}$ can be crucial for measuring the majority of the total angular momentum \citep[e.g.][]{Obreschkow2015,Harrison2017,Swinbank2017}.
This is similar to the measurement of the velocity at the radius enclosing 80$\%$ of the total light, $V_{80}$ ($\simeq3R_{D}$), \citep{Tiley2016a}.

@@

\subsubsection{Isolated field sample classification}\label{subsubsection:isolated_classification}
As mentioned above, various methods have been used throughout the literature to quantify the kinematic structure of star-forming galaxies at different redshifts. 
These include the kinemetry approach which quantifies aysmmetries in the 2D moment maps described in \cite{Shapiro2008} and applied throughout in \cite{ForsterSchreiber2009} and \cite{Cresci2009}.
In \cite{Wisnioski2015} a set of 5 criteria (see their section 4) identify rotationally dominated and disky galaxies by assessing the smoothness of the velocity gradient, the degree of rotational support through the ratio of the velocity to velocity dispersion, $V_{rot}/\sigma$, the $\Delta PA$ misalignment and the position of the kinematic centre in relation to both the peak in the velocity dispersion map and the centroid of the continuum centre (also see \cite{Rodrigues2016} for a re-analysis of KMOS$^{3D}$ data at z$\simeq1$ using the same criteria).   
In \cite{Epinat2012}, a detailed description of a morpho-kinematic classification is outlined in their section 4, based on the proximity of counterparts in the imaging, $\Delta PA$ and $V_{C}/\sigma_{int}$.
In \cite{Gnerucci2011} an inclined plane is fit to the velocity map and the $\chi^{2}$ of this fit is evaluated in order to test for the presence of smooth velocity gradients, which they find for the 11/33 galaxies described in Appendix \ref{subsec:AMAZE}.
We use a simple approach (dictated by the S/N of the isolated field sample) and calculate rotation and dispersion-dominated percentages on the basis of $V_{C}/\sigma_{int}$ alone with repsect to the total number of resolved galaxies in the field environment (38, see Table \ref{tab:pointings}).
The morphologically isolated KDS field galaxies are classified as rotation-dominated if $V_{C}/\sigma_{int} > 1$, 13/38 or 34\% of the sample, and dispersion-dominated if $V_{C}/\sigma_{int} < 1$, 19/38 or 50\% of the sample, as indicated in the final column of Table \ref{tab:kin_props}.
We plot the best fitting smeared and intrinsic models for the isolated field galaxies in Appendix \ref{app:kinematics_plots}, where the galaxies have been divided into rotation and dispersion-dominated categories in figures \ref{fig:rotation_dominated_galaxies} and \ref{fig:dispersion_dominated_galaxies} respectively.

@@

We plot the relationship between $V_{C}$ and $M_{\star}$ for the isolated field sample in the left panel of Figure \ref{fig:tf_relation}.
In \cite{Harrison2017}, the inverse stellar mass Tully-Fisher relation relation is fit to $\simeq400$ $9.5 < log(M_{\star}/M_{\odot}) < 10.5$ star-forming galaxies at $z\simeq0.9$, measured to be rotationally dominated with $V_{C}/\sigma_{int} > 1$.
The data are used to constrain parameters `a' and `b' in the equation $logV_{C}=b+a[logM_{\star} - 10.10]$ (see their section 4.2) finding $a = 0.33 \pm 0.11$ and $b = 2.12 \pm 0.04$.
We plot this best fit relation with the solid green line, with the green shaded region giving the typical scatter of 0.2 dex along the velocity axis.
These $z\simeq0.9$ parameters are consistent with the coefficients measured in the local universe, $a_{z=0} = 0.278 \pm 0.010$ and $b_{z=0} = 2.142 \pm 0.004$ , for a sample of $z<0.1$ disks from \cite{Reyes2011}, which are in a similar mass range to the KROSS galaxies in \cite{Harrison2017} and traced with H$\alpha$ emission.
In \cite{Reyes2011} $V_{C}$ has been extracted at the same radius and we plot this $z\simeq0.1$ local relation as the dashed black line in the left panel of Figure \ref{fig:tf_relation}.
The agreement between the parameters derived at $z\simeq0$ and $z\simeq0.9$ suggests that there is no evolution of the slope/normalisation of the stellar mass Tully-Fisher relation for rotationally dominated star-forming galaxies between these redshifts. \\

@@

Conclusions on the evolution of the stellar mass Tully-Fisher relation are a strong function of sample selection; in \cite{Tiley2016a} where a stricter $V_{C}/\sigma_{int} > 3$ cut is applied, evolution to lower masses at fixed rotation velocity is observed at $z\simeq0.9$, which is not the case when using the $V_{C}/\sigma_{int} > 1$ cut.
Similarly in \cite{Cresci2009} evolution of the normalisation of the stellar mass Tully-Fisher relation is observed at $z\simeq2$ using only robust rotators from the SINS sample with mean $V_{C}/\sigma_{int} = 5$.
In both cases the observed evolution is mainly the result of omitting rotationally dominated galaxies with lower $V_{C}$ values.
Conversely, fitting the stellar mass Tully-Fisher relation through a full sample including dispersion-dominated galaxies would shift the zero-point in the opposite sense.

@@

The KDS mean and median $V_{C}$ values are $76.7^{+4.9}_{-4.5}kms^{-1}$ and $57.0^{+6.6}_{-6.3}kms^{-1}$, both of which are below the $\left<V_{C}\right> = 125kms^{-1}$ limit.
The observation of a low mean $V_{C}$ value in the full isolated field sample is primarily explainable through averaging over a sample with a higher fraction of dispersion-dominated galaxies with lower rotation velocities.
This is seen in the left panel of Figure \ref{fig:tf_relation} where the dispersion-dominated galaxies sit clearly below and separated from the stellar mass Tully-Fisher relation.
However it has also been discussed that pressure support, provided by turbulence and measured through the galaxy velocity dispersions, may partially compensate the gravitational force within galaxy disks and contributes to lowering the rotation velocities through an `asymmetric drift' correction \citep[e.g.][]{Burkert2010,Newman2013,Genzel2017}.
This topic is discussed further throughout \cref{sec:discussion}.

@@

In \cite{Wisnioski2015} the authors present a scaling relation describing the increase of $\sigma_{int}$ with redshift in terms of the key observable properties $f_{gas}$, $t_{depl}$ and sSFR.
Using observed constraints for these properties from \cite{Tacconi2013} leads to $\sigma_{int}$ predictions that match the data remarkably well (see \cite{Wisnioski2015} figures 10 and 11).
The relation is an expression of the belief that high redshift galaxies experience more intense and efficient gas inflow, with the accumulation of a more massive stellar population providing stability against perturbations.
In this equilibrium model framework \citep[e.g.][]{Dave2012,Lilly2013,Saintonge2013}, populations of disk galaxies with higher average stellar mass have lower average velocity dispersions due to this stability condition.  \\

@@

The precise interpretation of the velocity dispersion remains unclear, although there is mounting evidence that random motions have an increasingly significant contribution to the mass budget of high redshift galaxies \citep[e.g.][]{Kassin2007,Law2009,Burkert2010,Kassin2012,Wuyts2016b,Lang2017,Ubler2017,Genzel2017}.
The nature of dispersion-dominated galaxies at high redshift has been discussed in \cite{Newman2013} using Adaptive-Optics (AO) and seeing limited observations of the same galaxies.
The AO observations show that in some cases galaxies which are clasified as dispersion-dominated with seeing limited observations reveal much larger velocity gradients at higher spatial resolution.
This highlights that beam-smearing effects can wash-out observed rotational motions, particularly for small galaxies.
We have attempted to account for beam smearing using half-light radius and velocity gradient dependent dynamical modelling, but we acknowledge that these observations are challenging and cannot rule out the presence of unresolved velocity gradients in our seeing-limited dataset.
Smaller galaxies do have intrinsically smaller rotation velocities, whilst there is no observed dependence of velocity dispersion on galaxy size \citep[e.g.][]{Newman2013}.
Dispersion-dominated galaxies are therefore likely to be at an earlier evolutionary stage and unstable to gravitational instabilities which generate turbulence which is then maintained by the potential energy of the gas in the disk \citep{Burkert2010,Newman2013}.

@@

CMH, AMS and RMS acknowledge the Science and Technology Facilities Council through grant code ST/L00075X/1.
RJM acknowledges the support of the European Research Council via the award of a Consolidator Grant (PI: McLure).
JSD acknowledges the support of the European Research Council via the award of an Advanced Grant (PI J. Dunlop), and the contribution of the EC FP7 SPACE project ASTRODEEP (Ref.No: 312725).
AMS acknowledges the Leverhulme Foundation.
JM acknowledges the support of a Huygens PhD fellowship from Leiden University. DS acknowledges financial support from the Netherlands Organization for Scientific research (NWO) through a Veni fellowship and from FCT through an FCT Investigator Starting Grant and Start-up Grant (IF/01154/2012/CP0189/CT0010).
This work is based on observations taken by the CANDELS Multi-Cycle Treasury Program with the NASA/ESA {\em HST}, which is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS5-26555.
This work is based on observations taken by the 3D-{\em HST} Treasury Program (GO 12177 and 12328) with the NASA/ESA {\em HST}, which is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS5-26555.
Based on data obtained with the European Southern Observatory Very Large Telescope, Paranal, Chile, under Large Program 185.A-0791, and made available by the VUDS team at the CESAM data center, Laboratoire d'Astrophysique de Marseille, France.
The {\em HST} data matched to the VUDS-DR1 are described in \cite{Grogin2011} and \cite{Koekemoer2011} for CANDELS and include data from the ERS \cite{Windhorst2011}.

@@

\section{Kinematics Plots}\label{app:kinematics_plots}
In figures \ref{fig:rotation_dominated_galaxies}, \ref{fig:dispersion_dominated_galaxies} and \ref{fig:merger_galaxies} we plot the kinematic grids for the KDS galaxies classified as rotation-dominated, dispersion-dominated and merger candidates respectively.
The figure captions provide more information on each of the panels of these grids.

@@

\begin{table*}
\centering
\begin{threeparttable}
\caption{We present here a reference of the mean and median kinematic properties used throughout figures \protect\ref{fig:tf_relation}, \protect\ref{fig:sigma_and_v_sigma_w_redshift} and \protect\ref{fig:rdf_and_v_sigma_w_redshift} for the different surveys.
The errors on the mean represent the statistical errors from bootstrap resampling and the lower and upper errors on the medians are the 16th and 84th percentiles of the distribution respectively.}
\label{tab:evolution_numbers}
\begin{tabular}{c c c c c c c c c c }

>>>>

\subsubsection{SED fitting and main-sequence}\label{subsubsec:sed_fitting}
In order to constrain their SFRs and stellar masses, the available photometry for the KDS targets was analysed using the SED fitting software described in \cite{McLure2011} and \cite{McLeod2015}.
The photometry for each target was fit with the same set of solar metallicity BC03 \citep{Bruzual2003} templates recommended for reproducing the properties of star-forming galaxies by \cite{Wuyts2011a}, and derived stellar masses and SFRs were based on a Chabrier IMF.
During the SED fitting process, dust attenuation was accounted for using the \cite{Calzetti2000} reddening law, with dust attenuation allowed to vary freely within the range $0.0<A_{V}<2.5$.
Based on the adopted template set, the median stellar mass for the full observed sample is $\log(M_{\star}/{\rm M}_{\odot}) = 10.0$. 
We note that fitting the photometry of the KDS targets with 0.2Z$\odot$ templates, rather than solar metallicity templates, typically reduces the derived stellar masses by $\simeq0.1$ dex, but this change does not affect the conclusions of this work.
In SSA22, 29 targets (36\% of the full KDS sample) do not have robust SFR measurements due to being undetected at $\geq 2\sigma$ significance in the available $J-$ and $K-$band photometry.
The median of the ratio of the derived stellar masses in GOODS-S to the matched stellar masses in \cite{Santini2015} (which presents an average result from 10 different sets of analyses) shows that the masses adopted here are $\simeq0.15$ dex larger. \\

@@

\subsubsection{Half-light radii}\label{subsubsection:half-light_radii}
The half-light radius, $R_{1/2}$, provides an indication of the disk sizes and hence gives us a common fiducial distance from the centre of the galaxy at which to extract rotation velocities.
As discussed throughout the introduction and in Appendix \ref{app:comparison_samples}, methods used to derive the intrinsic maximum circular velocity, $V_{C}$, vary widely between studies, and so to compare with previous work it is necessary to extract kinematic parameters consistently from the derived rotation curves.
Knowledge of $R_{1/2}$ gives a well defined and consistent point across the extent of the galaxy at which to extract velocities, which is important when making comparisons to previous IFU studies and see Appendix \ref{app:comparison_samples} and \citep[e.g.][]{ForsterSchreiber2009,Epinat2012,Wisnioski2015,Stott2016,Harrison2017,Swinbank2017}.
Throughout our dynamical modelling and beam-smearing correction (see \cref{subsec:3d_modelling}) we also require the $R_{1/2}$ value for each galaxy.
The median difference between the derived $R_{1/2}$ values and those presented in \cite{VanderWel2012} for the 22 matched GOODS-S galaxies is $\Delta R_{1/2} = 0.0054^{\prime\prime}$ (corresponding to 0.04kpc at $z\simeq3.5$).

@@

Each 0.1$^{\prime\prime}$ spaxel across a datacube is considered in turn.
The redshift value determined from fitting the [O~{\sc III}]$\lambda$5007 line in the integrated galaxy spectrum, $z_{sys}$, is used to determine the central wavelength of the redshifted [O~{\sc III}]$\lambda$5007 line, $\lambda_{obs_{5007}}$. 
We search a narrow region around $\lambda_{obs_{5007}}$ for the peak flux, assumed to correspond to the ionised gas emission, and extract a 5$\AA$ region (corresponding to 20 spectral elements) centred on this peak.
This truncated spectrum is then used in the fitting procedure for each spaxel.
The width of the extraction region is large enough to encompass unphysically large velocity shifts, but not so large as to compromise the fitting by potentially encompassing regions of the spectrum plagued by strong sky line residuals.
A single gaussian model is fit to the extraction region, again using {\tt LMFIT} \citep{Newville2014}, returning the values of the best-fitting flux, $F_{g}$, central wavelength, $\lambda_{g}$, and dispersion, $\sigma_{g}$.
These parameters, along with the estimate of the noise in the datacube, are used to assess whether the fitting of the [O~{\sc III}]$\lambda$5007 line is acceptable or not. 
The noise is estimated by masking all datacube spaxels containing object flux and computing the standard deviation of the flux values in the spectral extraction region for all remaining spaxels inwards of 0.3$^{\prime\prime}$ from the cube boundary (over the same spectral region as considered to find the peak object flux).
This boundary constraint is to mitigate edge effects, where the noise increases sharply due to fewer individual exposures constituting the final stack in these regions.
The final noise value is then taken as the standard deviation of the results from each unmasked spaxel, as shown in Equation \ref{eq:noise} where $F_{i,background}$ are the flux values across the spatial regions containing no object flux and the spectral extraction region and $N_{m}$ denotes noise estimated from masking the datacube.

@@

    \caption{We plot the kinematic grids for one rotation-dominated galaxy (top grid), one dispersion-dominated galaxy (middle grid) and one merger candidate (bottom grid) (see \protect\cref{subsec:morpho-kin-class}) from the KDS.
    In Appendix \protect\ref{app:kinematics_plots} we include these plots for each of the spatially-resolved galaxies in the KDS, divided into rotation-dominated, dispersion-dominated and merger categories.
    For each galaxy we plot on the top row the {\em HST} image, {\tt GALFIT} model and {\tt GALFIT} residuals, along with the observed [O~{\sc III}]$\lambda$5007 intensity map and velocity dispersion map. 
    On the bottom row we plot the observed velocity map, the beam-smeared model velocity and data-model velocity residuals with colour bar limits tuned to the velocity model.
    The solid black line and dashed orange line plotted in various panels show $PA_{kin}$ and $PA_{morph}$ respectively.
    Also on the bottom row, we plot extractions along $PA_{kin}$ for both the velocity and velocity dispersion.
    The grey points with errorbars on the velocity extraction plot are from the observed velocity map, the blue line and blue shaded regions represent the beam-smeared model fit to the data and errors respectively, whereas the red line and shaded regions are the intrinsic model from which $V_{C}$ is extracted.
    The purple symbols represent the extraction along $PA_{kin}$ from the residual map and the red and blue dashed lines denote the intrinsic and convolved $2R_{1/2}$ values respectively, with $V_{C}$ extracted at the intrinsic value and $V_{BS}$ extracted at the convolved value of the intrinsic and observed profiles respectively.
    The intrinsic models flatten at small radii, and so small changes in $R_{1/2}$ have negligible impact on the final, extracted $V_{C}$ values.
    The blue points on the velocity dispersion extraction plot show the values extracted from the observed dispersion map and the red are from the beam-smearing corrected map as per Equation \protect\ref{eq:dispersion_comp}.
    Also on the 1D dispersion plot we include with the blue and red dot-dash horizontal lines median values of the observed and intrinsic (i.e. $\sigma_{int}$) dispersion maps respectively.
    The merger candidate in the bottom grid requires several {\tt GALFIT} components to describe the data, mimics rotation from a purely kinematic perspective and we plot the 1D extractions without beam-smearing corrections, which are not warranted for multiple component objects.}
    \label{fig:main_body_kinematic_grids}

@@

The MCMC sampling provides a distribution of parameter values around those which give the maximum-likelihood.
We have confirmed also by examining the individual parameter chains that the MCMC run has been properly `burned-in' and that the parameter estimates have converged around the 50th percentile values.
The 16th and 84th percentiles of these distributions will be used to assess the model uncertainties as described in Appendix \ref{appsubsec:model_errors}.

@@

\subsubsection{Beam-smearing corrected rotation velocities}\label{subsubsec:beam_smearing_corrected_velocities}
The intrinsic velocity, $V_{C}$, is found by reading off from the best-fitting intrinsic 2D model grid at the intrinsic $2R_{1/2}$ value ($\simeq3.4R_{D}$, where $R_{D}$ is the scale length for an exponential disk).
This extraction radius is shown with the vertical red dashed line in the panels of Figure \ref{fig:main_body_kinematic_grids} showing the 1D velocity extraction.
The $V_{C}$ value extracted at $2R_{1/2}$ is a commonly used measure of the `peak' of the rotation curve \citep[e.g.][]{Miller2011,Stott2016,Pelliccia2017,Harrison2017,Swinbank2017} and extracting the velocity at $\geqslant 2R_{1/2}$ can be crucial for measuring the majority of the total angular momentum \citep[e.g.][]{Obreschkow2015,Harrison2017,Swinbank2017}.
This is similar to the measurement of the velocity at the radius enclosing 80$\%$ of the total light, $V_{80}$ ($\simeq3R_{D}$), \citep{Tiley2016a}.

@@

\subsubsection{Isolated field sample classification}\label{subsubsection:isolated_classification}
As mentioned above, various methods have been used throughout the literature to quantify the kinematic structure of star-forming galaxies at different redshifts. 
These include the kinemetry approach which quantifies aysmmetries in the 2D moment maps described in \cite{Shapiro2008} and applied throughout in \cite{ForsterSchreiber2009} and \cite{Cresci2009}.
In \cite{Wisnioski2015} a set of 5 criteria (see their section 4) identify rotation-dominated and disky galaxies by assessing the smoothness of the velocity gradient, the degree of rotational support through the ratio of the velocity to velocity dispersion, $V_{rot}/\sigma$, the $\Delta PA$ misalignment and the position of the kinematic centre in relation to both the peak in the velocity dispersion map and the centroid of the continuum centre (also see \cite{Rodrigues2016} for a re-analysis of KMOS$^{3D}$ data at z$\simeq1$ using the same criteria).   
In \cite{Epinat2012}, a detailed description of a morpho-kinematic classification is outlined in their section 4, based on the proximity of counterparts in the imaging, $\Delta PA$ and $V_{C}/\sigma_{int}$.
In \cite{Gnerucci2011} an inclined plane is fit to the velocity map and the $\chi^{2}$ of this fit is evaluated in order to test for the presence of smooth velocity gradients, which they find for the 11/33 galaxies described in Appendix \ref{subsec:AMAZE}.
We use a simple approach (dictated by the S/N of the isolated field sample) and calculate rotation and dispersion-dominated percentages on the basis of $V_{C}/\sigma_{int}$ alone with repsect to the total number of resolved galaxies in the field environment (38, see Table \ref{tab:pointings}).
The morphologically isolated KDS field galaxies are classified as rotation-dominated if $V_{C}/\sigma_{int} > 1$, 13/38 or 34\% of the sample, and dispersion-dominated if $V_{C}/\sigma_{int} < 1$, 19/38 or 50\% of the sample, as indicated in the final column of Table \ref{tab:kin_props}.
We plot the best-fitting smeared and intrinsic models for the isolated field galaxies in Appendix \ref{app:kinematics_plots}, where the galaxies have been divided into rotation and dispersion-dominated categories in Figures \ref{fig:rotation_dominated_galaxies} and \ref{fig:dispersion_dominated_galaxies} respectively.

@@

We plot the relationship between $V_{C}$ and $M_{\star}$ for the isolated field sample in the left panel of Figure \ref{fig:tf_relation}.
In \cite{Harrison2017}, the inverse stellar mass Tully-Fisher relation relation is fit to $\simeq400$ $9.5 < log(M_{\star}/M_{\odot}) < 10.5$ star-forming galaxies at $z\simeq0.9$, measured to be rotation-dominated with $V_{C}/\sigma_{int} > 1$.
The data are used to constrain parameters `a' and `b' in the equation $logV_{C}=b+a[logM_{\star} - 10.10]$ (see their section 4.2) finding $a = 0.33 \pm 0.11$ and $b = 2.12 \pm 0.04$.
We plot this best fit relation with the solid green line, with the green shaded region giving the typical scatter of 0.2 dex along the velocity axis.
These $z\simeq0.9$ parameters are consistent with the coefficients measured in the local universe, $a_{z=0} = 0.278 \pm 0.010$ and $b_{z=0} = 2.142 \pm 0.004$ , for a sample of $z<0.1$ disks from \cite{Reyes2011}, which are in a similar mass range to the KROSS galaxies in \cite{Harrison2017} and traced with H$\alpha$ emission.
In \cite{Reyes2011} $V_{C}$ has been extracted at the same radius and we plot this $z\simeq0.1$ local relation as the dashed black line in the left panel of Figure \ref{fig:tf_relation}.
The agreement between the parameters derived at $z\simeq0$ and $z\simeq0.9$ suggests that there is no evolution of the slope/normalisation of the stellar mass Tully-Fisher relation for rotation-dominated star-forming galaxies between these redshifts. \\

@@

Conclusions on the evolution of the stellar mass Tully-Fisher relation are a strong function of sample selection; in \cite{Tiley2016a} where a stricter $V_{C}/\sigma_{int} > 3$ cut is applied, evolution to lower masses at fixed rotation velocity is observed at $z\simeq0.9$, which is not the case when using the $V_{C}/\sigma_{int} > 1$ cut.
Similarly in \cite{Cresci2009} evolution of the normalisation of the stellar mass Tully-Fisher relation is observed at $z\simeq2$ using only robust rotators from the SINS sample with mean $V_{C}/\sigma_{int} = 5$.
In both cases the observed evolution is mainly the result of omitting rotation-dominated galaxies with lower $V_{C}$ values.
Conversely, fitting the stellar mass Tully-Fisher relation through a full sample including dispersion-dominated galaxies would shift the zero-point in the opposite sense.

@@

The KDS mean and median $V_{C}$ values are $76.7^{+4.9}_{-4.5}kms^{-1}$ and $57.0^{+6.6}_{-6.3}kms^{-1}$, both of which are below the $\left<V_{C}\right> = 125kms^{-1}$ limit.
The observation of a low mean $V_{C}$ value in the full isolated field sample is primarily explainable through averaging over a sample with a higher fraction of dispersion-dominated galaxies with lower rotation velocities.
This is seen in the left panel of Figure \ref{fig:tf_relation} where the dispersion-dominated galaxies sit clearly below and separated from the stellar mass Tully-Fisher relation.
However it has also been discussed that pressure support, provided by turbulence and measured through the galaxy velocity dispersions, may partially compensate the gravitational force within galaxy disks and contributes to lowering the rotation velocities through an `asymmetric drift' correction \citep[e.g.][]{Burkert2010,Newman2013,Genzel2017}.
This topic is discussed further throughout \cref{sec:discussion}. \\\\

@@

In \cite{Wisnioski2015} the authors present a scaling relation describing the increase of $\sigma_{int}$ with redshift in terms of the key observable properties $f_{gas}$, $t_{depl}$ and sSFR.
Using observed constraints for these properties from \cite{Tacconi2013} leads to $\sigma_{int}$ predictions that match the data remarkably well (see \cite{Wisnioski2015} Figures 10 and 11).
The relation is an expression of the belief that high redshift galaxies experience more intense and efficient gas inflow, with the accumulation of a more massive stellar population providing stability against perturbations.
In this equilibrium model framework \citep[e.g.][]{Dave2012,Lilly2013,Saintonge2013}, populations of disk galaxies with higher average stellar mass have lower average velocity dispersions due to this stability condition.  \\

@@

The precise interpretation of the velocity dispersion remains unclear, although there is mounting evidence that random motions have an increasingly significant contribution to the mass budget of high redshift galaxies \citep[e.g.][]{Kassin2007,Law2009,Burkert2010,Kassin2012,Wuyts2016b,Lang2017,Ubler2017,Genzel2017}.
The nature of dispersion-dominated galaxies at high redshift has been discussed in \cite{Newman2013} using Adaptive-Optics (AO) and seeing limited observations of the same galaxies.
The AO observations show that in some cases galaxies which are clasified as dispersion-dominated with seeing limited observations reveal much larger velocity gradients at higher spatial resolution.
This highlights that beam-smearing effects can wash-out observed rotational motions, particularly for small galaxies.
We have attempted to account for beam-smearing using half-light radius and velocity gradient dependent dynamical modelling, but we acknowledge that these observations are challenging and cannot rule out the presence of unresolved velocity gradients in our seeing-limited dataset.
Smaller galaxies do have intrinsically smaller rotation velocities, whilst there is no observed dependence of velocity dispersion on galaxy size \citep[e.g.][]{Newman2013}.
Dispersion-dominated galaxies are therefore likely to be at an earlier evolutionary stage and unstable to gravitational instabilities which generate turbulence which is then maintained by the potential energy of the gas in the disk \citep{Burkert2010,Newman2013}.

@@

CMH, AMS and RMS acknowledge the Science and Technology Facilities Council through grant code ST/L00075X/1.
RJM acknowledges the support of the European Research Council via the award of a Consolidator Grant (PI: McLure).
JSD acknowledges the support of the European Research Council via the award of an Advanced Grant (PI J. Dunlop), and the contribution of the EC FP7 SPACE project ASTRODEEP (Ref.No: 312725).
AMS acknowledges the Leverhulme Foundation.
JM acknowledges the support of a Huygens PhD fellowship from Leiden University. DS acknowledges financial support from the Netherlands Organization for Scientific research (NWO) through a Veni fellowship and from FCT through an FCT Investigator Starting Grant and Start-up Grant (IF/01154/2012/CP0189/CT0010).
This work is based on observations taken by the CANDELS Multi-Cycle Treasury Program with the NASA/ESA {\em HST}, which is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS5-26555.
This work is based on observations taken by the 3D-{\em HST} Treasury Program (GO 12177 and 12328) with the NASA/ESA {\em HST}, which is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS5-26555.
Based on data obtained with the European Southern Observatory Very Large Telescope, Paranal, Chile, under Large Program 185.A-0791, and made available by the VUDS team at the CESAM data center, Laboratoire d'Astrophysique de Marseille, France.

@@

@@

\begin{table*}
\centering
\begin{threeparttable}
\caption{The mean and median kinematic properties used throughout Figures \protect\ref{fig:tf_relation}, \protect\ref{fig:sigma_and_v_sigma_w_redshift} and \protect\ref{fig:rdf_and_v_sigma_w_redshift} for the different surveys.
The errors on the mean represent the statistical errors from bootstrap resampling and the lower and upper errors on the medians are the 16th and 84th percentiles of the distribution respectively.}
\label{tab:evolution_numbers}
\begin{tabular}{llllllllll}
